---
title: "Covid 19 Prediction in India"
author: "Mohamed Ashmil KT"
date: "26/06/2021"
output:
  html_document:
    df_print: paged
---

Covid 19 Future Prediction in India

Loading needed Libraries and loading the dataset
```{r}
pacman::p_load(covid19.analytics,dplyr,prophet,lubridate,ggplot2)
covid_data= covid19.data(case='ts-confirmed')
```
Filterling out the data of India and Checking the data
```{r}
asd=covid_data%>%
  filter(Country.Region=="India")
str(asd)
type_of(asd)
class(asd)
```

Data Cleaning
```{r}
#converting rows into columns
asd=data.frame(t(asd))



#change the date from index to a variable
asd=cbind(asd,ds=rownames(asd),row.names=NULL)
asd=asd[,c(2,1)]

#renaming column
colnames(asd)=c("ds","y")

#removing other rows than date and case
asd=asd[-c(1:4),]

str(asd)
#specifying R the order of date is y-m-d
asd$ds=ymd(asd$ds)
asd$y=as.numeric(asd$y)

str(asd)
```

Plotting the data to see the struture
```{r}
plot(asd)
qplot(ds,y,data = asd, main = "Covid in India")
```

Forcasting
```{r}
m=prophet(asd) #we don't have enough data to capture seasonality
```
we don't have enough data to capture seasonality

Prediction
Making a data frame for future 28 days with the given data
```{r}
future=make_future_dataframe(m,periods = 28,freq = "day",include_history = T)
forecast=predict(m,future)
```

Ploting the Forcast
```{r}
plot(m,forecast)
dyplot.prophet(m,forecast)
```

Finding the forecast components
```{r}
prophet_plot_components(m, forecast)
```

Model Perfomance
```{r}
pred=forecast$yhat[1:521]
actual= m$history$y
plot(actual, pred)
abline(lm(pred~actual),col="blue")
```

Checking Summary to see accuracy
```{r}
summary(lm(pred~actual))
```